Kyoto VR MQP Paper First Draft

### 2019-09-25 paper.tex

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to Editour'' card provides these instructions, which should be
enough to get started.  A user can only terminate the polygon after two points
have been placed to prevent the user from drawing a region with an area of
zero. Once a region is created, a region card appears in the side bar. From
here, the user can edit anything about the region. From here, the user can edit
anything about the region.

@@

The third subcard is the ``Delete'' subcard. When revelead, another button will
appear labeled ``Really Delete''. The action can be canceled by collapsing the
subcard by hitting the bar now labeled ``Don't Delete!''. This prevents the user
from accidentally deleting a region he or she did not mean to.

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process. If a 200 or 201 is returned from the
server, a ``Success'' message will appear. If there was some problem, the error
message returned by the server is displayed in this box instead. Since
uploading, downloading and deleting are all network-related operations, it
makes sense to include this message box for each card.

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking on
one of these blue buttons will fill the textbox in with the correct name. Before
this feature was implemented, the user had to correctly type the name of the
saved tour into the textbox in order to retrieve it. The user is still free to
do this, but the buttons make this easier and less error-prone.

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button. We also hard-coded some shortcuts for places that Atticus
might want to design a tour for in the future, which can be accessed by
clicking on the yellow buttons with place names.

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps \autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience..
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

As previously mentioned, Atticus initially wanted us to explore the efficacy of
using Vuforia's 2D image target capabilities for scanning objects outside of
the expected use case, such as 3D landscapes or the side of a building. We had
serious doubts about how well this would work, and our suspicions were
confirmed after some field testing. This was the reasoning behind focusing on
ground-plane detection instead of image targets; ground-plane detection can be
used anywhere, and is much more reliable than treating 3D objects as 2D image
targets.

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store, called ``Experience Importer - Adobe Xd files importer'', which claims
``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
objects. They're already there! Just drag .xd file to project and... voila!''
We suspect this sounds too good to be true because it is. As of September
20\textsuperscript{th}, 2019, there are 6 user reviews. All of the five-star
reviews were have the caveat ``Reviewer was gifted package by publisher'' which
which we interpreted as a warning sign. Because of this, we decided to rebuild
the UI largely from the ground up, using the Adobe XD file to guide us.

>>>>

The user can easily create a new region by shift-clicking, and then clicking
points on the map.  To terminate the polygon, the user must shift-click again.
The ``Welcome to Editour'' card (seen in Figure~\ref{fig:welcomeCard}) provides
these instructions, which should be enough to get started.  A user can only
terminate the polygon after two points have been placed to prevent the user
from drawing a region with an area of zero. Once a region is created, a region
card appears in the side bar. From here, the user can edit anything about the
region. From here, the user can edit anything about the region.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{welcome-card-editour.png}
    \caption{The ``Welcome to Editour'' card providing basic instructions to
    get started}
	\label{fig:welcomeCard}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{drawing-region-editour.png}
    \caption{How the Editour looks when a region is being drawn, including the
    two dotted preview lines}
	\label{fig:drawingRegion}
\end{figure}

@@

\begin{figure}[h]
	\centering
    \includegraphics[width=\textwidth]{edit-subcard-with-map-editour.png}
    \caption{The ``Edit'' subcard with the map showing vertices and edges that
    can be edited}
	\label{fig:editSubcardWithMap}
\end{figure}

The third subcard pictured in Figure~\ref{fig:deleteSubcard} is the ``Delete''
subcard. When revealed, another button will appear labeled ``Really Delete''.
The action can be canceled by collapsing the subcard by hitting the bar now
labeled ``Don't Delete!''. This prevents the user from accidentally deleting a
region he or she did not mean to.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{delete-subcard-editour.png}
    \caption{The ``Delete'' subcard}
	\label{fig:deleteSubcard}
\end{figure}

Above all of the region cards, there are various options for uploading,
downloading, renaming and deleting tour files on the server. Within the upload,
download and delete cards there are message boxes to indicate the status of
that operation. When uploading and downloading, a percentage will be displayed
indicating the upload/download process, which can be seen in
Figure~\ref{fig:uploadingMessage}. If a 200 or 201 is returned from the server,
a ``Success'' message will appear. If there was some problem, the error message
returned by the server is displayed in this box instead. Since uploading,
downloading and deleting are all network-related operations, it makes sense to
include this message box for each card.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{uploading-message-editour.png}
    \caption{The upload subcard with an upload status}
	\label{fig:uploadingMessage}
\end{figure}

When the page is loaded, the frontend will request the names of the files
stored on the server from the backend. This data is used to create a box of
buttons, which includes one button for each tour file on the server. Clicking
on one of these blue buttons will fill the textbox in with the correct name.
Before this feature was implemented, the user had to correctly type the name of
the saved tour into the textbox in order to retrieve it. The user is still free
to do this, but the buttons make this easier and less error-prone. The download
card containing a box filled with filenames on the server can be seen in
Figure~\ref{fig:downloadCard}.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{download-card-editour.png}
    \caption{The download card}
	\label{fig:downloadCard}
\end{figure}

We did not include a way to resolve addresses or place names, like the service
provided by Google Maps. Instead of exploring plugins/libraries that might
provide this functionality, we offered a simpler solution due to time
constraints.  You can type in a latitude and longitude directly and hit the
``Jump'' button. We also hard-coded a few shortcuts for places that Atticus
might want to design a tour for in the future, which can be accessed by
clicking on the yellow buttons with place names.

\begin{figure}[h]
	\centering
    \includegraphics[width=0.4\textwidth]{jump-card-editour.png}
    \caption{The jump card}
	\label{fig:jumpCard}
\end{figure}

@@

At this point, the codebase for Editour was already around three thousand lines
of vanilla JavaScript. Type-checking provided by Visual Studio Code and JSDoc
made the growing code complexity more manageable. Excluding Node.js modules,
the only external library we used for Editour was Leaflet, an open-source
JavaScript library for interactive maps \autocite{leafletjs}. We did not use
any libraries for developing frontends like Facebook's React or Google's
Angular. Instead, all of the complex UI interactions were handled by modifying
the DOM directly with JavaScript's built-in functionality. Furthermore, we did
not use any advanced frontend build tools such as Rollup, webpack or Parcel.
This was likely an appropriate decision for a JavaScript project of this scope.
Considering we had limited to no experience with React or Angular, it was also
faster to develop the UI in the way we were used to from previous experience.
But if we were to continue to develop Editour, UI libraries and frontend build
tools would be something to consider. With these changing requirements, the
Editour was becoming onerous to maintain at this stage of the project.

@@

Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the expected use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

Since Adobe XD is largely a prototyping and design tool, a considerable amount
of legwork would still need to be done to rebuild the proposed design using
Unity's UI components. Adobe XD allowed us to export a few important UI
elements as PNGs, such as the buttons to enter AR mode and view the map. We
briefly explored a few solutions to automating the task of getting the Adobe XD
project into Unity. We found one payed extension (for \$18) on the Unity Asset
store, called ``Experience Importer - Adobe Xd files importer'', which claims
``Transfer AdobeXd project directly to Unity. Forget about hours of positioning
objects. They're already there! Just drag .xd file to project and...
voila!''~\autocite{glasseye2019}.  We suspect this sounds too good to be true
because it is. As of September 20\textsuperscript{th}, 2019, there are 6 user
reviews. All of the five-star reviews were have the caveat ``Reviewer was gifted
package by publisher'' which which we interpreted as a warning sign. Because of
this, we decided to rebuild the UI largely from the ground up, using the Adobe XD
file to guide us.
